Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-22 ms.tex
changing the description of the efficiency.

\citet{Sharma+2007} calculate the radiative efficiency, $\epsilon$,
based on MHD shearing box simulations of collisionless plasmas. For
accretion rates $10^{-4} \lsim \eddr \lsim 10^{-2}$, the radiative
efficiency is $\epsilon_{\rm rad}\sim 2.6\%$\footnote{for $\eddr\lsim
  10^{-4} \epsilon_{\rm rad}\sim \eddr^{0.9}$. For $\eddr\gg 0.01$
  $\epsilon_{\rm rad}\sim 0.1$...}. Additionally, a large
fraction of the $\dot{M}$ on large scales will be driven out in
outflows as the gas has some non-zero angular momentum and a
centrifugal barrier will stop it from accreting \citet{Li+2013}. In
the limit weak cooling appropriate for low accretion rates the
accretion rate on small scales will be of order $\alpha \Mdot$. Here
we adopt $\alpha=0.1$ so that our overall efficiency is 0.26\%

@@

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} Average nuclear X-ray luminosity, $\langle
  L_X \rangle = \epsilon_X \Mdot c^2$, as a function of SMBH mass.
  Green lines show our prediction in the case of heating due to the
  average SFH for galaxies corresponding to each black hole mass
  (Fig.~\ref{fig:bh_growth}), calculated using a power-law fit for the
  relationship $\Gamma(M_{\bullet})$ derived from the
  \citet{LauerFaber+:2007a} sample.  Shown for comparison are the
  measurements ({\it black stars}) and upper limits ({\it gray
    triangles}) for $L_X/L_{\rm edd}$ values, from the
  \citet{Miller+15} sample of early-type galaxies (a black line shows
  the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto
  M_{\bullet}^{\alpha}$, with $\alpha = -0.2$).  The left panel is
  calculated assuming a constant radiative efficiency
  $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand
  panel assumes $\epsilon_X= 0.01 (\epsilon_{\rm bol}/0.1)
  (\alpha/0.1) \epsilon_{rad} (\eddr) $, where $\epsilon_{\rm
    rad}\simeq 0.026$ for $\lsim 10^{-4} \eddr\lsim 10^{-2} $, as
  motivated by shearing box simulations of collisionless plasma (see
  \citet{Sharma+2007}).  Shown for comparison are the X-ray
  luminosities calculated for the maximum thermally-stable accretion
  rate ({\it dashed orange line}; eq.~[\ref{eq:Mdotmax}]); the SN
  Ia-regulated accretion rate ({\it dashed teal line};
  eq.~[\ref{eq:eddr_Ia}]), and the Compton heating-regulated accretion
  rate ({\it dashed pink line}; eq.~[\ref{eq:MdotCa}]), again all
  calculated for the average SFH corresponding to each SMBH mass.}
\end{figure*}

>>>>

\citet{Sharma+2007} calculate the radiative efficiency, $\epsilon$,
based on MHD shearing box simulations of collisionless plasmas. The
following piecewise power law approximately reproduces
their results for the radiative efficiency, $\epsilon_{\rm rad}$

\begin{align}
\epsilon_{\rm rad} \simeq 
\begin{cases}
  2.6 \times 10^{-2} \left(\eddr\right)^{0.9} & \eddr \lsim 10^{-4} \\
  2.6 \times 10^{-2} &  10^{-2} \lsim \eddr \lsim  10^{-4}\\
  0.1 \left(\eddr\right)^{0.58} &  10^{-2} \lsim \eddr \lsim  0.1\\
  0.1 & \eddr \gsim 0.1
\end{cases}
\label{eq:efficiency}
\end{align}

The first two lines are a piecewise power law fit designed to
approximately reproduce the solid line in Figure 6
in \citet{Sharma+2007}, which assumes 33\% of the viscous dissipation
heats the electrons. For $\eddr\gsim 0.1$, $\epsilon_{rad}$ should saturate
to 0.1, hence the fourth line. The third line is a power law which
connects $\epsilon_{\rm rad} (\eddr=0.01) = 0.026$ to $\epsilon_{\rm
  rad} (\eddr=0.1) = 0.1$.

Additionally, a large fraction of the $\dot{M}$ on large scales will
be driven out in outflows as the gas has some non-zero angular
momentum and a centrifugal barrier will stop it from accreting
\citet{Li+2013}. In the limit weak cooling appropriate for low
accretion rates the accretion rate on small scales will be of order
$\alpha \Mdot$.  Taking $epsilon=\alpha \epsilon_{\rm rad}$ for the
overall efficiency with $\alpha=0.1$ and $\epsilon_{\rm rad}$ from
equation~\eqref{eq:efficiency} we obtain {\bf AG note the change in
  the description of the efficiency},

@@

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} Average nuclear X-ray luminosity, $\langle
  L_X \rangle = \epsilon_X \Mdot c^2$, as a function of SMBH mass.
  Green lines show our prediction in the case of heating due to the
  average SFH for galaxies corresponding to each black hole mass
  (Fig.~\ref{fig:bh_growth}), calculated using a power-law fit for the
  relationship $\Gamma(M_{\bullet})$ derived from the
  \citet{LauerFaber+:2007a} sample.  Shown for comparison are the
  measurements ({\it black stars}) and upper limits ({\it gray
    triangles}) for $L_X/L_{\rm edd}$ values, from the
  \citet{Miller+15} sample of early-type galaxies (a black line shows
  the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto
  M_{\bullet}^{\alpha}$, with $\alpha = -0.2$).  The left panel is
  calculated assuming a constant radiative efficiency
  $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand
  panel assumes $\epsilon_X= 0.01 (\epsilon_{\rm bol}/0.1)
  (\alpha/0.1) \epsilon_{rad} (\eddr) $, where $\epsilon_{\rm rad}$ is
  given by equation~\eqref{eq:efficiency}.  Shown for comparison are
  the X-ray luminosities calculated for the maximum thermally-stable
  accretion rate ({\it dashed orange line}; eq.~[\ref{eq:Mdotmax}]);
  the SN Ia-regulated accretion rate ({\it dashed teal line};
  eq.~[\ref{eq:eddr_Ia}]), and the Compton heating-regulated accretion
  rate ({\it dashed pink line}; eq.~[\ref{eq:MdotCa}]), again all
  calculated for the average SFH corresponding to each SMBH mass.}
\end{figure*}
